\documentclass{article}

\usepackage[letterpaper, portrait, margin=1.5in]{geometry}

\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{rotating}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

\setcounter{secnumdepth}{1}

\usepackage{chngcntr}
\counterwithin{figure}{section}

\renewcommand*{\thepage}{C\arabic{page}}

\pagestyle{fancy}
\lhead{ACME Robotics}
\chead{\#8367}
\rhead{\ifcontents Contents \else Week \thesection \fi}

\newif\ifcontents
\contentstrue

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

\begin{document}\contentsfalse
\subsection{Discuss Gracious Professionalism}
%! Discuss the important FIRST value of Gracious Professionalism with both teams.
Although ACME members from last year were well versed in the ways of Gracious Professionalism, the new members - and ARES members - were not. As Gracious Professionalism is the underlining value of FIRST, Emma and Kelly decided to give a presentation on the subject. Pulling up a Google Slides presentation in the Drive, Emma was able to write a fairly comprehensive guide on how to be a Gracious Professional. After having Kelly read it over, and spending some time developing the Flowers Dialectic, Kelly presented it to both teams. The teams had a great discussion about how and how not to behave at competition, as well as how to be a Gracious Professional in their everyday life. The only thing this presentation could not totally explain was how rewarding it can be to practice these values. The team especially saw this last year at the Northern California Regionals, when they helped their friends, team 5214: Tech Support, by buying them an emergency servo. The team ended up being on the winning alliance because of it.  

\end{document}