\documentclass{article}

\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{rotating}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

\setcounter{secnumdepth}{1}

\usepackage{chngcntr}
\counterwithin{figure}{section}

\renewcommand*{\thepage}{C\arabic{page}}

\pagestyle{fancy}
\lhead{ACME Robotics}
\chead{\#8367}
\rhead{\ifcontents Contents \else Week \thesection \fi}

\newif\ifcontents
\contentstrue

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

\begin{document}\contentsfalse

\subsection{Write the summary and cover pages for the Business and Engineering Notebooks}
%! Finish up the BN by printing the summary and cover pages.
As the tournament draws closer, finishing the Business Notebook becomes ever more important. Even though the notebook itself was already printed, a cover page and summary page was still needed to complete the task. Emma worked on the summary page this year. The summary page is not only an introduction to the team's mission, it is where specific parts of the notebook worth noting can be found, as well as specific events. Emma adapted the summary page the team used last year by rewriting the team's story and mission for this year, altering the season highlights, and choosing specific topics of interest in the notebook. The season highlights are notable events that are exciting or great accomplishments of the team. The team's overlying goal for this year is to maintain the FIRST program in our community and train members on our team so that ACME can keep going in the future. The summary also mentioned goals on how the team wants to progress to Worlds again this year. With these things complete, the BN is now complete.  



\end{document}