\documentclass{article}

\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{rotating}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

\setcounter{secnumdepth}{1}

\usepackage{chngcntr}
\counterwithin{figure}{section}

\renewcommand*{\thepage}{C\arabic{page}}

\pagestyle{fancy}
\lhead{ACME Robotics}
\chead{\#8367}
\rhead{\ifcontents Contents \else Week \thesection \fi}

\newif\ifcontents
\contentsfalse

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

\begin{document}

\subsection{Draft and discuss this season's budget}
%!Draft budgets for the Software and Hardware Teams to determine fundraising goals and whether or not we can afford two competition robots.
In preparation for the coming season, Kellen and Ryan devised two budgets for the Hardware and Software Teams respectively. For the Hardware team, the budget consisted primarily of planned purchases of Tetrix parts, tools, and motors/servos. For the Software Team, the budget was mainly concerned with buying new phones and migrating to the new REV control system. As a group, we tallied the estimated expenses and profits for team membership fees and determined our fundraising goals for this year based on travel/registration costs from previous seasons, which was six thousand dollars. We also decided that we had enough money and resources to build two competition robots this season. See Appendix A in the Business Notebook for more details.

\subsection{Complete fundraising and thank you letters}
%!Write two letters, one to last year's sponsors thanking them for supporting us, the other requesting funds from new and old sponsors.
This week Emma and Clara worked on writing two letters to our sponsors.  The first was a thank you letter, written to last year's sponsors thanking them for all of their generous support during last season. The second was the fundraising letter sent to various potential and current sponsors asking for donations for the coming season. The letters can be seen in Appendix B of the Business Notebook. The letter included our new system of donations, which uses tiers to provide the sponsor with varied levels of publicity on our website and social media. These tiers can provide the sponsor with anything from a shout out on social media to a private presentation of the robot.  These tiers are to provide the donor with a clear description of what they will receive if they fund us. The letters will be sent out to local businesses and companies. 

\end{document}