\documentclass{article}

\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{rotating}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

\setcounter{secnumdepth}{1}

\usepackage{chngcntr}
\counterwithin{figure}{section}

\renewcommand*{\thepage}{C\arabic{page}}

\pagestyle{fancy}
\lhead{ACME Robotics}
\chead{\#8367}
\rhead{\ifcontents Contents \else Week \thesection \fi}

\newif\ifcontents
\contentstrue

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

\begin{document}\contentsfalse
\subsection{Continue work on the Business Notebook}
%!Finish the budget, goals and action plan, and the finishing touches on outreach events.
It was very important to the team to print the Business Notebook at least 24 hours before the team left for the tournament. This meant that in order to meet that goal most of the big stuff that needed to be put into the Business Notebook (budget, goals and action plan, etc.) needed to be done quickly. Emma worked on writing up these things in the BN this week. First, she finalized the budget with the other team captains and mentors and added a few additional expenses such as the cost of the field. Then she put all of this information into a table that could be easily read and understood. For the goals and action plan Emma worked with Stephanie to come up with a new way to display the team's plans for the future. Basically, each goal is listed and given a short summary, then the plans to meet that goal are written in bullet form and then several paragraphs below that illustrate how the team is working to complete the goal or the results of that plan. Emma also added a section to the outreach events about future events that the team is planning. Such events include a presentation to the local Girls Who Code club, a meet up with a VEX robotics team in the county and a workshop with the Girl Scouts. (For more information on these events and other outreach events, please peruse the Business Notebook). 

\end{document}
