\documentclass{article}

\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{rotating}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

\setcounter{secnumdepth}{1}

\usepackage{chngcntr}
\counterwithin{figure}{section}

\renewcommand*{\thepage}{C\arabic{page}}

\pagestyle{fancy}
\lhead{ACME Robotics}
\chead{\#8367}
\rhead{\ifcontents Contents \else Week \thesection \fi}

\newif\ifcontents
\contentstrue

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

\begin{document}\contentsfalse

\subsection{Work on the Business Notebook}
%! There is much to be done for the BN, so work on it must start immediately.
The team realized that there was a lot of work that needed to be done on the Business Notebook, so Emma decided to take on that task. The BN includes all of the team's outreach events, the sustainability plan, our goals and action plans, team bios, fundraising information, current sponsor list, etc. With so much to, Emma decided to start with the team bios as those just needed to be typed in \LaTeX . Although there were plenty of answers to questions she and Kelly had asked team members the week before, she only chose 4 or 5 for each bio so that they only filled one page and would leave room for a picture. After the bios were completed, Emma started to write up the outreach events ACME did at the end of last season and over the summer. ACME had been writing about four paragraphs about each outreach event, which Emma thought was a bit excessive. So, she came up with a new format. A picture from the event is at the top of the page followed by the title for the event. A short summary sentence is after that, then bullet points highlighting parts of the event that explain what the team did, how it effected the team and how it benefited the people who the team helped or presented to. She found this method to be much more concise and easy to read. Next week, Emma plans to continue work on the BN by finalizing the budget and writing up the teams goals and action plans. 
\end{document}